Handbook streamFind: backend

### 2022-10-04 handbooks/Handbook_backend_streamFind.Rmd
LFU15
Creation of global import namespace
LFU16_small fixes 2

r_path <- system.file(package = "streamFindData", dir = "extdata")

@@

```{r}
#as a named vector
meta_1 <- c("water", TRUE, "centroid")
names(meta_1) <- c("matrix", "spiked", "datatype")

>>>>

r_path <- system.file(package = "streamFindData", dir = "extdata")
#r_path <- system.file(package = "streamFind", dir = "extdata")

@@

```{r add-metadata-msdata}
#as a named vector
meta_1 <- c("water", TRUE, "centroid")
names(meta_1) <- c("matrix", "spiked", "datatype")
